---
title: "Bracket"
author: "Alex Connolly"
date: "3/15/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 3

## The Bracket! 

Awesome, now just knit this document/run the code and it will generate the winners. Be sure to fill your bracket out starting in each round with the West region, then the East, then the South, then the Midwest.

```{r library, include=FALSE}
library(rvest)
library(implied)
library(tidyverse)
library(odds.converter)
library(robotstxt)
```


```{r Wprob, includ=FALSE}
Weighted_Probabilities <- function(PT1, team_name_1, PT2, team_name_2){Pbin = (PT1 *100)/(PT1*100 + PT2*100)
New_Variable <- print(rbinom(1, 1, prob=Pbin))
if(New_Variable){
  print(team_name_1)
return(c(PT1, team_name_1))
}else{
    print(team_name_2)
return(c(PT2,team_name_2))
}}
```

### Round of 64 Winners

```{r set, include=FALSE}
Houston <- 0.1257154 
Alabama <- 0.08874031 
Kansas <- 0.05802251 
Purdue <- 0.05802251 
UCLA <- 0.05802251 
Gonzaga <- 0.04714329
Arizona <- 0.04714329 
Texas <- 0.04714329 
Marquette <- 0.03969961 
UConn <- 0.03428603 
Tennessee <- 0.02901125 
Baylor <- 0.02901125
Duke <- 0.02218508 
Kentucky <- 0.02095257 
Creighton <- 0.02095257 
TCU <- 0.01839738  
Saint_Marys <- 0.01639767 
Xavier <- 0.01479005
Indiana <- 0.01346951 
Texas_AM <- 0.01346951 
Virginia <- 0.01236545 
Iowa_State <- 0.01236545    
Michigan_State <- 0.01142868   
Kansas_State <- 0.01142868
San_Diego_State <- 0.009924903 
Miami <- 0.009924903 
Memphis <- 0.009924903 
Iowa <- 0.009924903   
West_Virginia <- 0.009924903
Illinois <- 0.007468244 
Arkansas <- 0.007468244 
Maryland <- 0.005757959      
Florida_Atlantic <- 0.005757959 
Providence <- 0.004995315
USC <- 0.004995315 
Auburn <- 0.004995315 
Penn_State <- 0.004995315 
NC_State <- 0.0037527    
Northwestern <- 0.0037527  
Utah_State <- 0.0037527
Pittsburgh <- 0.002783368 
Drake <- 0.002148982 
Missouri <- 0.002148982 
Boise_State <- 0.002148982 
VCU <- 0.001672489 
Iona <- 0.001505574
Vermont <- 0.001505574   
Arizona_State <- 0.001505574 
Nevada <- 0.001505574 
Colgate <- 0.001505574  
Oral_Roberts <- 0.001505574
Charleston <- 0.001505574 
Kent_State <- 0.001505574 
Furman <- 0.001505574         
Fairleigh_Dickinson <- 0.001505574  
UNC_Asheville <- 0.001505574
Kennesaw_State <- 0.001505574       
Northern_Kentucky <- 0.001505574 
Louisiana <- 0.001505574 
Texas_AM_CC <- 0.001505574   
Montana_State <- 0.001505574
Howard <- 0.001505574    
Texas_Southern <- 0.001505574      
UC_Santa_Barbara <- 0.001505574  
Grand_Canyon <- 0.001505574 
Princeton <- 0.001505574
```

```{r Round64}
W1 <- Weighted_Probabilities(Alabama, "Alabama", Texas_AM_CC, "TX AM CC")
W2 <- Weighted_Probabilities(Maryland, "Maryland", West_Virginia, "West Virginia")
W3 <- Weighted_Probabilities(San_Diego_State, "San Diego St.", Charleston, "Charleston")
W4 <- Weighted_Probabilities(Virginia, "Virginia", Furman, "Furman")
W5 <- Weighted_Probabilities(Creighton, "Creighton", NC_State, "NC State")
W6 <- Weighted_Probabilities(Baylor, "Baylor", UC_Santa_Barbara, "UCSB")
W7 <- Weighted_Probabilities(Missouri, "Missouri", Utah_State, "Utah St.")
W8 <- Weighted_Probabilities(Arizona, "Arizona", Princeton, "Princeton")
W9 <- Weighted_Probabilities(Purdue, "Purdue", Fairleigh_Dickinson, "FDU")
W10 <- Weighted_Probabilities(Memphis, "Memphis", Florida_Atlantic, "FAU")
W11 <- Weighted_Probabilities(Duke, "Duke", Oral_Roberts, "Oral Roberts")
W12 <- Weighted_Probabilities(Tennessee, "Tennessee", Louisiana, "Louisiana")
W13 <- Weighted_Probabilities(Kentucky, "Kentucky", Providence, "Providence")
W14 <- Weighted_Probabilities(Kansas_State, "Kansas St.", Montana_State, "Montana St.")
W15 <- Weighted_Probabilities(Michigan_State, "Michigan St.", USC, "USC")
W16 <- Weighted_Probabilities(Marquette, "Marquette", Vermont, "Vermont")
W17 <- Weighted_Probabilities(Houston, "Houston", Northern_Kentucky, "N. Kentucky")
W18 <- Weighted_Probabilities(Iowa, "Iowa Hall", Auburn, "Auburn")
W19 <- Weighted_Probabilities(Miami, "Miami", Drake, "Drake")
W20 <- Weighted_Probabilities(Indiana, "Indiana", Kent_State, "Kent St.")
W21 <- Weighted_Probabilities(Iowa_State, "Iowa St.", Pittsburgh, "Pittsburgh")
W22 <- Weighted_Probabilities(Xavier, "Xavier", Kennesaw_State, "Kennesaw St.")
W23 <- Weighted_Probabilities(Texas_AM, "Texas AM", Penn_State, "Penn St.")
W24 <- Weighted_Probabilities(Texas, "Texas", Colgate, "Colgate")
W25 <- Weighted_Probabilities(Kansas, "Kansas", Howard, "Howard")
W26 <- Weighted_Probabilities(Arkansas, "Arkansas", Illinois, "Illinois")
W27 <- Weighted_Probabilities(Saint_Marys, "Saint Mary's", VCU, "VCU")
W28 <- Weighted_Probabilities(UConn, "UConn", Iona, "Iona")
W29 <- Weighted_Probabilities(TCU, "TCU", Arizona_State, "ASU")
W30 <- Weighted_Probabilities(Gonzaga, "Gonzaga", Grand_Canyon, "Grand Canyon")
W31 <- Weighted_Probabilities(Northwestern, "Northwestern", Boise_State, "Boise St.")
W32 <- Weighted_Probabilities(UCLA, "UCLA", UNC_Asheville, "UNC-Ash")
```
### Round of 32 Winners

```{r Round32}
W33 <- Weighted_Probabilities(as.numeric(W1[1]), W1[2], as.numeric(W2[1]), W2[2])
W34 <- Weighted_Probabilities(as.numeric(W3[1]), W3[2], as.numeric(W4[1]), W5[2])
W35 <- Weighted_Probabilities(as.numeric(W5[1]), W5[2], as.numeric(W6[1]), W6[2])
W36 <- Weighted_Probabilities(as.numeric(W7[1]), W7[2], as.numeric(W8[1]), W8[2])
W37 <- Weighted_Probabilities(as.numeric(W9[1]), W9[2], as.numeric(W10[1]), W10[2])
W38 <- Weighted_Probabilities(as.numeric(W11[1]), W11[2], as.numeric(W12[1]), W12[2])
W39 <- Weighted_Probabilities(as.numeric(W13[1]), W13[2], as.numeric(W14[1]), W14[2])
W40 <- Weighted_Probabilities(as.numeric(W15[1]), W15[2], as.numeric(W16[1]), W16[2])
W41 <- Weighted_Probabilities(as.numeric(W17[1]), W17[2], as.numeric(W18[1]), W18[2])
W42 <- Weighted_Probabilities(as.numeric(W19[1]), W19[2], as.numeric(W20[1]), W20[2])
W43 <- Weighted_Probabilities(as.numeric(W21[1]), W21[2], as.numeric(W22[1]), W22[2])
W44 <- Weighted_Probabilities(as.numeric(W23[1]), W23[2], as.numeric(W24[1]), W24[2])
W45 <- Weighted_Probabilities(as.numeric(W25[1]), W25[2], as.numeric(W26[1]), W26[2])
W46 <- Weighted_Probabilities(as.numeric(W27[1]), W27[2], as.numeric(W28[1]), W28[2])
W47 <- Weighted_Probabilities(as.numeric(W29[1]), W29[2], as.numeric(W30[1]), W30[2])
W48 <- Weighted_Probabilities(as.numeric(W31[1]), W31[2], as.numeric(W32[1]), W32[2])
```

### Sweet 16 Winners

```{r Sweet16}
W49 <- Weighted_Probabilities(as.numeric(W33[1]), W33[2], as.numeric(W34[1]), W34[2])
W50 <- Weighted_Probabilities(as.numeric(W35[1]), W35[2], as.numeric(W36[1]), W36[2])
W51 <- Weighted_Probabilities(as.numeric(W37[1]), W37[2], as.numeric(W38[1]), W38[2])
W52 <- Weighted_Probabilities(as.numeric(W39[1]), W39[2], as.numeric(W40[1]), W40[2])
W53 <- Weighted_Probabilities(as.numeric(W41[1]), W41[2], as.numeric(W42[1]), W42[2])
W54 <- Weighted_Probabilities(as.numeric(W43[1]), W43[2], as.numeric(W44[1]), W44[2])
W55 <- Weighted_Probabilities(as.numeric(W45[1]), W45[2], as.numeric(W46[1]), W46[2])
W56 <- Weighted_Probabilities(as.numeric(W47[1]), W47[2], as.numeric(W48[1]), W48[2])
```

### Elite 8 Winners

```{r Elite8}
W57 <- Weighted_Probabilities(as.numeric(W49[1]), W49[2], as.numeric(W50[1]), W50[2])
W58 <- Weighted_Probabilities(as.numeric(W51[1]), W51[2], as.numeric(W52[1]), W52[2])
W59 <- Weighted_Probabilities(as.numeric(W53[1]), W53[2], as.numeric(W54[1]), W54[2])
W60 <- Weighted_Probabilities(as.numeric(W55[1]), W55[2], as.numeric(W56[1]), W56[2])
```

### Final Four Winners

```{r Final4}
W61 <- Weighted_Probabilities(as.numeric(W57[1]), W57[2], as.numeric(W58[1]), W58[2])
W62 <- Weighted_Probabilities(as.numeric(W59[1]), W59[2], as.numeric(W60[1]), W60[2])
```

### Championship Winner

```{r Finals}
W63 <- Weighted_Probabilities(as.numeric(W61[1]), W61[2], as.numeric(W62[1]), W62[2])
```


Thanks for using this bracket generator, hope you win!