---
title: "Bracket"
author: "Alex Connolly"
date: "3/15/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 3

## The Bracket! 

Awesome, now just knit this document/run the code and it will generate the winners. Be sure to fill your bracket out starting in each round with the West region, then the East, then the South, then the Midwest.

```{r library, include=FALSE}
library(rvest)
library(implied)
library(tidyverse)
library(odds.converter)
library(robotstxt)
```


```{r Wprob, includ=FALSE}
Weighted_Probabilities <- function(PT1, team_name_1, PT2, team_name_2){Pbin = (PT1 *100)/(PT1*100 + PT2*100)
New_Variable <- print(rbinom(1, 1, prob=Pbin))
if(New_Variable){
  print(team_name_1)
return(c(PT1, team_name_1))
}else{
    print(team_name_2)
return(c(PT2,team_name_2))
}}
```

### Round of 64 Winners

```{r set, include=FALSE}
UConn <- 0.213
Houston <- 0.154 
Purdue <- 0.125
Arizona <- 0.077
NorthCarolina <- 0.053 
Tennessee <- 0.053
Auburn <- 0.053
IowaState <- 0.048
Creighton <- 0.038 
Marquette <- 0.038 
Duke <- 0.032 
Kentucky <- 0.032
Baylor <- 0.028
Illinois <- 0.028
Alabama <- 0.024 
Gonzaga <- 0.022 
Kansas <- 0.020
BYU <- 0.016
Wisconsin <- 0.016
Florida <- 0.015 
MichiganState <- 0.015
SaintMarys <- 0.015   
SDSU <- 0.013  
UNM <- 0.013
TexasTech <- 0.012
Texas <- 0.01
Colorado <- 0.009 
Clemson <- 0.008  
TCU <- 0.008
Nebraska <- 0.008 
WashingtonState <- 0.007
TexasAM <- 0.007    
MississippiState <- 0.007 
FloridaAtlantic <- 0.007
Dayton <- 0.007
ColoradoState <- 0.007 
Oregon <- 0.005
SouthCarolina <- 0.005 
Nevada <- 0.005
Utah_State <- 0.005
Drake <- 0.005
NcState <- 0.004 
Northwestern <- 0.004 
JMU <- 0.004
GrandCanyon <- 0.002 
McNeese <- 0.002
Yale <- 0.002
Samford <- 0.002
Vermont <- 0.002
UAB <- 0.001
Charleston <- 0.001
Morehead <- 0.001
Longwood <- 0.001505574 
Stetson <- 0.001505574         
Oakland <- 0.001505574  
Wagner <- 0.001505574
SouthDakotaState <- 0.001505574       
Colgate <- 0.001505574 
Akron <- 0.001505574 
WesternKentucky <- 0.001505574   
LongBeach <- 0.001505574
Grambling <- 0.001505574    
Duquense <- 0.001505574    
St.Peters <-0.001505574
```

```{r Round64}
W1 <- Weighted_Probabilities(UConn, "UConn", Stetson, "Stetson")
W2 <- Weighted_Probabilities(FloridaAtlantic, "FAU", Northwestern, "Northwestern")
W3 <- Weighted_Probabilities(SDSU, "San Diego St.", UAB, "UAB")
W4 <- Weighted_Probabilities(Auburn, "Auburn", Yale, "Yale")
W5 <- Weighted_Probabilities(BYU, "BYU", Duquense, "Duquense")
W6 <- Weighted_Probabilities(Illinois, "Illinois", Morehead, "Morehead")
W7 <- Weighted_Probabilities(WashingtonState, "Wash State", Drake, "Drake")
W8 <- Weighted_Probabilities(IowaState, "Iowa St", SouthDakotaState, "SDSU")
W9 <- Weighted_Probabilities(NorthCarolina, "UNC", Wagner, "Wagner")
W10 <- Weighted_Probabilities(MississippiState, "MissSt", MichiganState, "MSU")
W11 <- Weighted_Probabilities(SaintMarys, "St Marys", GrandCanyon, "Grand Canyon")
W12 <- Weighted_Probabilities(Alabama, "Alabama", Charleston, "Charleston")
W13 <- Weighted_Probabilities(Clemson, "Clemson", UNM, "UNM")
W14 <- Weighted_Probabilities(Baylor, " Baylor", Colgate, "Colgate")
W15 <- Weighted_Probabilities(Dayton, "Dayton", Nevada, "Nevada")
W16 <- Weighted_Probabilities(Arizona, "Arizona", LongBeach, "Long Beach")
W17 <- Weighted_Probabilities(Houston, "Houston", Longwood, "Longwood")
W18 <- Weighted_Probabilities(Nebraska, "Nebraska", TexasAM, "TexasAM")
W19 <- Weighted_Probabilities(Wisconsin, "Wisconsin", JMU, "JMU")
W20 <- Weighted_Probabilities(Duke, "Duke", Vermont, "Vermont")
W21 <- Weighted_Probabilities(TexasTech, "Texas Tech", NcState, "NC State")
W22 <- Weighted_Probabilities(Kentucky, "Kentucky", Oakland, "Oakland")
W23 <- Weighted_Probabilities(Florida, "Florida", Colorado, "Colorado")
W24 <- Weighted_Probabilities(Marquette, "Marquette", WesternKentucky, "Western Kentucky")
W25 <- Weighted_Probabilities(Purdue, "Purdue", Grambling, "Grambling")
W26 <- Weighted_Probabilities(Utah_State, "Utah State", TCU, "TCU")
W27 <- Weighted_Probabilities(Gonzaga, "Gonzaga", McNeese, "McNeese")
W28 <- Weighted_Probabilities(Kansas, "Kansas", Samford, "Samford")
W29 <- Weighted_Probabilities(SouthCarolina, "South Carolina", Oregon, "Oregon")
W30 <- Weighted_Probabilities(Creighton, "Creighton", Akron, "Akron")
W31 <- Weighted_Probabilities(Texas, "Texas", ColoradoState, "Colorado St")
W32 <- Weighted_Probabilities(Tennessee, "Tennessee", St.Peters, "St. Peters")
```
### Round of 32 Winners

```{r Round32}
W33 <- Weighted_Probabilities(as.numeric(W1[1]), W1[2], as.numeric(W2[1]), W2[2])
W34 <- Weighted_Probabilities(as.numeric(W3[1]), W3[2], as.numeric(W4[1]), W4[2])
W35 <- Weighted_Probabilities(as.numeric(W5[1]), W5[2], as.numeric(W6[1]), W6[2])
W36 <- Weighted_Probabilities(as.numeric(W7[1]), W7[2], as.numeric(W8[1]), W8[2])
W37 <- Weighted_Probabilities(as.numeric(W9[1]), W9[2], as.numeric(W10[1]), W10[2])
W38 <- Weighted_Probabilities(as.numeric(W11[1]), W11[2], as.numeric(W12[1]), W12[2])
W39 <- Weighted_Probabilities(as.numeric(W13[1]), W13[2], as.numeric(W14[1]), W14[2])
W40 <- Weighted_Probabilities(as.numeric(W15[1]), W15[2], as.numeric(W16[1]), W16[2])
W41 <- Weighted_Probabilities(as.numeric(W17[1]), W17[2], as.numeric(W18[1]), W18[2])
W42 <- Weighted_Probabilities(as.numeric(W19[1]), W19[2], as.numeric(W20[1]), W20[2])
W43 <- Weighted_Probabilities(as.numeric(W21[1]), W21[2], as.numeric(W22[1]), W22[2])
W44 <- Weighted_Probabilities(as.numeric(W23[1]), W23[2], as.numeric(W24[1]), W24[2])
W45 <- Weighted_Probabilities(as.numeric(W25[1]), W25[2], as.numeric(W26[1]), W26[2])
W46 <- Weighted_Probabilities(as.numeric(W27[1]), W27[2], as.numeric(W28[1]), W28[2])
W47 <- Weighted_Probabilities(as.numeric(W29[1]), W29[2], as.numeric(W30[1]), W30[2])
W48 <- Weighted_Probabilities(as.numeric(W31[1]), W31[2], as.numeric(W32[1]), W32[2])
```

### Sweet 16 Winners

```{r Sweet16}
W49 <- Weighted_Probabilities(as.numeric(W33[1]), W33[2], as.numeric(W34[1]), W34[2])
W50 <- Weighted_Probabilities(as.numeric(W35[1]), W35[2], as.numeric(W36[1]), W36[2])
W51 <- Weighted_Probabilities(as.numeric(W37[1]), W37[2], as.numeric(W38[1]), W38[2])
W52 <- Weighted_Probabilities(as.numeric(W39[1]), W39[2], as.numeric(W40[1]), W40[2])
W53 <- Weighted_Probabilities(as.numeric(W41[1]), W41[2], as.numeric(W42[1]), W42[2])
W54 <- Weighted_Probabilities(as.numeric(W43[1]), W43[2], as.numeric(W44[1]), W44[2])
W55 <- Weighted_Probabilities(as.numeric(W45[1]), W45[2], as.numeric(W46[1]), W46[2])
W56 <- Weighted_Probabilities(as.numeric(W47[1]), W47[2], as.numeric(W48[1]), W48[2])
```

### Elite 8 Winners

```{r Elite8}
W57 <- Weighted_Probabilities(as.numeric(W49[1]), W49[2], as.numeric(W50[1]), W50[2])
W58 <- Weighted_Probabilities(as.numeric(W51[1]), W51[2], as.numeric(W52[1]), W52[2])
W59 <- Weighted_Probabilities(as.numeric(W53[1]), W53[2], as.numeric(W54[1]), W54[2])
W60 <- Weighted_Probabilities(as.numeric(W55[1]), W55[2], as.numeric(W56[1]), W56[2])
```

### Final Four Winners

```{r Final4}
W61 <- Weighted_Probabilities(as.numeric(W57[1]), W57[2], as.numeric(W58[1]), W58[2])
W62 <- Weighted_Probabilities(as.numeric(W59[1]), W59[2], as.numeric(W60[1]), W60[2])
```

### Championship Winner

```{r Finals}
W63 <- Weighted_Probabilities(as.numeric(W61[1]), W61[2], as.numeric(W62[1]), W62[2])
```


Thanks for using this bracket generator, hope you win!